Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-09 Ben_Manuscripts/structure_paper/supporting_information.tex
Figure updates
New figures

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

\SectionNumbersOn

\externaldocument[M-]{draft}
%MRS8: can use document class here - looks weird with title/authors as written.
\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

%  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

@@

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
          %MRS8: nm to aa conversion error?
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
	  8 \AA   & $0.69 \pm 0.01$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{The average pore radii of systems built with an initial pore
		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
		  the pore radius is too large, slit pores may form.}~\label{table:radii}
	  \end{table}

@@

%  \begin{figure}
%	\centering
%	\begin{subfigure}{0.45\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{ps5layered.png}
%		\caption{}\label(fig:ps5layered}
%	\end{subfigure}
%	\begin{subfigure}
%		\centering
%		\includegraphics[width=\textwidth]{ps5offset.png}
%		\caption{}\label{fig:ps5offset}
%	\end{subfigure}
%  \end{figure}

  \begin{figure}[!htb]
        \centering
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \hspace{-1cm}
%                \vspace{1cm}
%                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
%                \caption{}\label{fig:tails_topview}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{tails_rzplot.png}
%                \caption{}\label{fig:tails_rzplot}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=0.5\textwidth]{centroids_box.png}
		\caption{Monomer tails pack together hexagonally. The centroid
			of each tail is visualized as a blue sphere. The centroids are calculated based
			on the red atoms in Figure~\ref{fig:monomer_color_coded}. The red sphere
			highlights an example of an alkane tail centroid with its nearest neighbors
			(green spheres) surrounding it in a hexagonal pattern.}\label{fig:centroids}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{angles_traj_layered.png}
%                \caption{}\label{fig:angle_distribution}
%        \end{subfigure}
%        \caption{(a) The trajectory can be stripped of all atoms except carbon
%        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
%        still gives rise to R-spots. (c) Finding the center of mass and visualizing
%        their coordinates reveals the hexagonal-like packing of the tails. (d) The
%        distribution created by measuring the angle between each centroid (e.g. red
%        in (c)) and its nearest neighbors (e.g. green in (c)) with respect to the xy
%        plane has distinct spikes near 30\degree, which is consistent with the location
%        of R-spots}\label{fig:tail_packing}
  \end{figure}

>>>>

%\documentclass[journal=jpcbfk,manuscript=article]{achemso}
\documentclass{article}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

%\SectionNumbersOn

\externaldocument[M-]{draft}
\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

@@

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  2.5 \AA & $4.0 \pm 0.1$ \AA \\
	  5 \AA   & $4.2 \pm 0.1$ \AA \\
	  8 \AA   & $6.9 \pm 0.1$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{The average pore radii of systems built with an initial pore
		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
		  the pore radius is too large, slit pores may form.}~\label{table:radii}
	  \end{table}

@@

%  \begin{figure}
%	\centering
%	\begin{subfigure}{0.45\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{ps5layered.png}
%		\caption{}\label(fig:ps5layered}
%	\end{subfigure}
%	\begin{subfigure}
%		\centering
%		\includegraphics[width=\textwidth]{ps5offset.png}
%		\caption{}\label{fig:ps5offset}
%	\end{subfigure}
%  \end{figure}
  \section{Tail organization}

  In order to understand the origin of R-spots, we looked for ordering among
  the tails. We divided the tail into three sections: tail fronts, tail 
  middles and tail ends. The sections are illustrated in 
  Figure~\ref{fig:tail_sections}.

  We plotted the center of masses of each tail section and measured the angle 
  between each center of mass and its nearest neighbor center of masses of the
  same tail section. For example, Figure~\ref{fig:centroids} shows a 3D plot of
  the center of masses of each tail front. We wanted to know average location
  of nearest neighbors to each center of mass. The red bead in 
  Figure~\ref{fig:centroids} is a randomly selected center of mass. The
  green beads are the nearest neighbor center of masses to the red bead. We
  measured the angle between the red bead and each green bead with respect to
  the $xy$ plane. We repeated the same calculation for each center of mass at
  each simulation frame and were able to plot the average distribution shown
  in Figure~\ref{fig:tail_fronts}. We repeated the calculation for the tail
  middles (Figure~\ref{fig:tail_middles}) and the tail ends 
  (Figure~\ref{fig:tail_ends}). The amount of order decreases as we explore
  packing of tails farther from the head group.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{tail_sections}
  \caption{We divided the tail into three regions: tail-fronts (blue), 
  tail-middles (green) and tail-backs (red).}\label{fig:tail_sections}
  \end{figure}

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{centroids.png}
		\caption{}\label{fig:centroids}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing.png}
        \caption{}\label{fig:tail_fronts}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_middles.png}
        \caption{}\label{fig:tail_middles}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_ends.png}
        \caption{}\label{fig:tail_ends}
        \end{subfigure}
        \caption{Monomer tails pack together hexagonally. (a) The center of mass
        of each tail-front (See Figure~\ref{fig:tail_sections}) is visualized as
        a blue sphere. The red sphere highlights an example of a tail-front 
        center of mass with its nearest neighbors (green spheres) surrounding it
        in a hexagonal pattern. (b) We calculated the angle between each tail-front
        center of mass and its nearest neighbor tail-front center of masses and 
        plotted the distribution. There are distinct peaks ca. $-60\degree$, $0\degree$ and
        $60\degree$ which is indicitive of hexagonal packing. (c) We repeated the 
        same procedure outlined in (a) and (b) with the tail-middles. There is still 
        a high degree of order. (d) We repeated the procedure again with the tail-ends.
        There is far less order at the ends of the tails where there is more
        space to fill.}\label{fig:tail_packing}
  \end{figure}
